---
title: "Unmodeled DIF in Latent Class Analysis: Consequences for Class Enumeration"
author: ""
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(glue)
library(MplusAutomation)
library(here)
library(gt)
library(janitor)
library(gridExtra)
library(ggpubr)
library(parallel)
library(cowplot)
library(effectsize)
library(broom)
library(tools)
library(apaTables)
library(patchwork)
```


# Enumeration Tables

*Note*: The last column in the enumeration tables in VLMR is NA, which indicates no nonsignificant *p*-value was found for that condition across replications.

## Realistic

### Complex

```{r, echo = FALSE, eval = TRUE}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(3.19064, 3.10788, 3.83448, 3.86343, 2.00700, 2.92895, 1.43653, 2.75844, 3.01256, 1.89987),
  C2 = c(1.16631, -0.15619, 3.77549, -0.51226, -1.58301, 0.11202, -2.15707, 0.57930, -0.28985, -0.19538),
  C3 = c(-0.56244, -0.06104, -0.74264, 0.58389, -1.44290, -15.0, 0.17762, 2.74127, 1.67876, 2.60714),
  C4 = c(-2.13783, -3.46779, -3.17454, -2.12725, -2.57868, -3.62206, -3.27125, -0.67695, -1.86035, -1.42219),
  C5 = c(-0.69130, -1.27803, -0.05214, 1.48891, 1.99572, 1.75719, -0.18973, 1.46395, 0.41521, 0.38082)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:10)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Realistic Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )+
  facet_wrap(~Class)

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Realistic Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
```


```{r, eval = FALSE, include= FALSE}
source(here("functions","process_enum"))
model_name <- "complex"
sep_cond <- "realistic"

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p1", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p1m1 <- valid_reps(parent_dir)
enum_table_com_p1m1 <- calculate_accuracy_com(extracted_index_com_p1m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p2", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p2m1 <- valid_reps(parent_dir) 
enum_table_com_p2m1 <- calculate_accuracy_com(extracted_index_com_p2m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p2", "m2", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p2m2 <- valid_reps(parent_dir) 
enum_table_com_p2m2 <- calculate_accuracy_com(extracted_index_com_p2m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p3", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p3m1 <- valid_reps(parent_dir) 
enum_table_com_p3m1 <- calculate_accuracy_com(extracted_index_com_p3m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p3", "m2", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p3m2 <- valid_reps(parent_dir) 
enum_table_com_p3m2 <- calculate_accuracy_com(extracted_index_com_p3m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p3", "m3", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p3m3 <- valid_reps(parent_dir) 
enum_table_com_p3m3 <- calculate_accuracy_com(extracted_index_com_p3m3) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p4", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p4m1 <- valid_reps(parent_dir) 
enum_table_com_p4m1 <- calculate_accuracy_com(extracted_index_com_p4m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p4", "m2", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p4m2 <- valid_reps(parent_dir) 
enum_table_com_p4m2 <- calculate_accuracy_com(extracted_index_com_p4m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p4", "m3", "realistic")
# Extracted summary of all replications across folders
extracted_index_com_p4m3 <- valid_reps(parent_dir) 
enum_table_com_p4m3 <- calculate_accuracy_com(extracted_index_com_p4m3) 
```

```{r, eval = FALSE, include= FALSE}
# Save files
total_com1 <- as.data.frame(rbind(enum_table_com_p1m1$combined_percentages, 
                                  enum_table_com_p2m1$combined_percentages,
                                  enum_table_com_p2m2$combined_percentages))  %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

total_com2 <- as.data.frame(rbind(enum_table_com_p3m1$combined_percentages, 
                                  enum_table_com_p3m2$combined_percentages, 
                                  enum_table_com_p3m3$combined_percentages,
                                  enum_table_com_p4m1$combined_percentages, 
                                  enum_table_com_p4m2$combined_percentages, 
                                  enum_table_com_p4m3$combined_percentages)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(total_com1, here("tables", "real_com1.csv"))
#write_csv(total_com2, here("tables", "real_com2.csv"))
```

*Note*: The last column in VLMR is NA, which indicates no nonsignificant p-value was found for that condition across replications.

```{r}
source(here("functions","process_enum"))
total_com1 <- read_csv(here("tables", "real_com1.csv")) %>% 
  select(-sim_model) 
  

total_com2 <- read_csv(here("tables", "real_com2.csv")) %>% 
  select(-sim_model) %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))

table_com1 <- gt_table_com(total_com1)
table_com2 <- gt_table_com(total_com2)

table_com1
table_com2

#gtsave(table_com1, here("tables", "table_com1.docx"))
#gtsave(table_com2, here("tables", "table_com2.docx"))
```

### Simple

```{r, echo = FALSE, eval = TRUE}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(-2.1, -2.120, -2.737, -4.172, -1.591, -3.187),
  C2 = c(-.2, -0.329, -0.127, -1.199, 1.591, 1.710),
  C3 = c(-1.5, -0.738, 0.888, 0.964, 0.039, -15.000),
  C4 = c(1, 1.547, 3.910, 2.382, 3.483, 15.000)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:6)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Realistic Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  ) +
  facet_wrap(~Class)


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Realistic Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  ) 
```


```{r, eval = FALSE, include= FALSE}
source(here("functions","process_enum"))

# Define the parent directory containing all folders
model_name <- "simple"
sep_cond <- "realistic"

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p1", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p1m1 <- valid_reps(parent_dir)
enum_table_sim_p1m1 <- calculate_accuracy_sim(extracted_index_sim_p1m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p2", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p2m1 <- valid_reps(parent_dir) 
enum_table_sim_p2m1 <- calculate_accuracy_sim(extracted_index_sim_p2m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p2", "m2", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p2m2 <- valid_reps(parent_dir) 
enum_table_sim_p2m2 <- calculate_accuracy_sim(extracted_index_sim_p2m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p3", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p3m1 <- valid_reps(parent_dir) 
enum_table_sim_p3m1 <- calculate_accuracy_sim(extracted_index_sim_p3m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p3", "m2", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p3m2 <- valid_reps(parent_dir) 
enum_table_sim_p3m2 <- calculate_accuracy_sim(extracted_index_sim_p3m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p3", "m3", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p3m3 <- valid_reps(parent_dir) 
enum_table_sim_p3m3 <- calculate_accuracy_sim(extracted_index_sim_p3m3) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p4", "m1", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p4m1 <- valid_reps(parent_dir) 
enum_table_sim_p4m1 <- calculate_accuracy_sim(extracted_index_sim_p4m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p4", "m2", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p4m2 <- valid_reps(parent_dir) 
enum_table_sim_p4m2 <- calculate_accuracy_sim(extracted_index_sim_p4m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p4", "m3", "realistic")
# Extracted summary of all replications across folders
extracted_index_sim_p4m3 <- valid_reps(parent_dir) 
enum_table_sim_p4m3 <- calculate_accuracy_sim(extracted_index_sim_p4m3) 
```

```{r, eval = FALSE, include= FALSE}
# Save Files
total_sim1 <- as.data.frame(rbind(enum_table_sim_p1m1$combined_percentages, 
                                  enum_table_sim_p2m1$combined_percentages, 
                                  enum_table_sim_p2m2$combined_percentages)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

total_sim2 <- as.data.frame(rbind(enum_table_sim_p3m1$combined_percentages, 
                                  enum_table_sim_p3m2$combined_percentages, 
                                  enum_table_sim_p3m3$combined_percentages,
                                  enum_table_sim_p4m1$combined_percentages, 
                                  enum_table_sim_p4m2$combined_percentages, 
                                  enum_table_sim_p4m3$combined_percentages))%>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(total_sim1, here("tables", "real_sim1.csv"))
#write_csv(total_sim2, here("tables", "real_sim2.csv"))
```

*Note*: The last column in VLMR is NA, which indicates no nonsignificant p-value was found for that condition across replications.

```{r}
source(here("functions","process_enum"))
total_sim1 <- read_csv(here("tables", "real_sim1.csv")) %>% 
  select(-sim_model)

total_sim2 <- read_csv(here("tables", "real_sim2.csv")) %>% 
  select(-sim_model) %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))


table_sim1 <- gt_table_sim(total_sim1)
table_sim2 <- gt_table_sim(total_sim2)

table_sim1
table_sim2

#gtsave(table_sim1, here("tables", "table_sim1.docx"))
#gtsave(table_sim2, here("tables", "table_sim2.docx"))
```

## Ideal

### Complex

```{r, echo = FALSE, eval = TRUE}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(-2,-2,-2,-2,-2,-2,-2,-2,-2,-2),
  C2 = c(-2,-2,-2,-2,-2,2,2,2,2,2),
  C3 = c(2,2,2,-2,-2,-2,2,2,2,2),
  C4 = c(2,2,2,2,2,-2,-2,-2,-2,-2),
  C5 = c(2,2,2,2,2,2,2,2,2,2)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:10)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")

# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "High Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  ) 

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "High Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  ) +
  facet_wrap(~Class)
```

```{r, eval = FALSE, include= FALSE}
source(here("functions","process_enum"))

model_name <- "complex"
sep_cond <- "ideal"

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p1", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p1m1 <- valid_reps(parent_dir)
enum_table_com_p1m1 <- calculate_accuracy_com(extracted_index_com_p1m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p2", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p2m1 <- valid_reps(parent_dir) 
enum_table_com_p2m1 <- calculate_accuracy_com(extracted_index_com_p2m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p2", "m2", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p2m2 <- valid_reps(parent_dir) 
enum_table_com_p2m2 <- calculate_accuracy_com(extracted_index_com_p2m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p3", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p3m1 <- valid_reps(parent_dir) 
enum_table_com_p3m1 <- calculate_accuracy_com(extracted_index_com_p3m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p3", "m2", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p3m2 <- valid_reps(parent_dir) 
enum_table_com_p3m2 <- calculate_accuracy_com(extracted_index_com_p3m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p3", "m3", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p3m3 <- valid_reps(parent_dir) 
enum_table_com_p3m3 <- calculate_accuracy_com(extracted_index_com_p3m3) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p4", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p4m1 <- valid_reps(parent_dir) 
enum_table_com_p4m1 <- calculate_accuracy_com(extracted_index_com_p4m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p4", "m2", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p4m2 <- valid_reps(parent_dir) 
enum_table_com_p4m2 <- calculate_accuracy_com(extracted_index_com_p4m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "complex", "p4", "m3", "ideal")
# Extracted summary of all replications across folders
extracted_index_com_p4m3 <- valid_reps(parent_dir) 
enum_table_com_p4m3 <- calculate_accuracy_com(extracted_index_com_p4m3) 
```

```{r, eval = FALSE, include= FALSE}
# Save files
total_com1 <- as.data.frame(rbind(enum_table_com_p1m1$combined_percentages, 
                                  enum_table_com_p2m1$combined_percentages,
                                  enum_table_com_p2m2$combined_percentages))  %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

total_com2 <- as.data.frame(rbind(enum_table_com_p3m1$combined_percentages, 
                                  enum_table_com_p3m2$combined_percentages, 
                                  enum_table_com_p3m3$combined_percentages,
                                  enum_table_com_p4m1$combined_percentages, 
                                  enum_table_com_p4m2$combined_percentages, 
                                  enum_table_com_p4m3$combined_percentages)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(total_com1, here("tables", "ideal_com1.csv"))
#write_csv(total_com2, here("tables", "ideal_com2.csv"))
```

*Note*: The last column in VLMR is NA, which indicates no nonsignificant p-value was found for that condition across replications.

```{r}
source(here("functions","process_enum"))
total_com1 <- read_csv(here("tables", "ideal_com1.csv")) %>% 
  select(-sim_model)

total_com2 <- read_csv(here("tables", "ideal_com2.csv")) %>% 
  select(-sim_model) %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))

table_com1 <- gt_table_com(total_com1)
table_com2 <- gt_table_com(total_com2)

table_com1
table_com2

#gtsave(table_com1, here("tables", "table_com1.docx"))
#gtsave(table_com2, here("tables", "table_com2.docx"))
```

### Simple

```{r, echo = FALSE, eval = TRUE}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(-2,-2,-2,-2,-2,-2),
  C2 = c(-2,-2,-2,2,2,2),
  C3 = c(2,2,2,-2,-2,-2),
  C4 = c(2,2,2,2,2,2)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:6)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Ideal Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )+
  facet_wrap(~Class)

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Ideal Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
```


```{r, eval = FALSE, include= FALSE}
source(here("functions","process_enum"))

# Define the parent directory containing all folders
model_name <- "simple"
sep_cond <- "ideal"

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p1", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p1m1 <- valid_reps(parent_dir)
enum_table_sim_p1m1 <- calculate_accuracy_sim(extracted_index_sim_p1m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p2", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p2m1 <- valid_reps(parent_dir) 
enum_table_sim_p2m1 <- calculate_accuracy_sim(extracted_index_sim_p2m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p2", "m2", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p2m2 <- valid_reps(parent_dir) 
enum_table_sim_p2m2 <- calculate_accuracy_sim(extracted_index_sim_p2m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p3", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p3m1 <- valid_reps(parent_dir) 
enum_table_sim_p3m1 <- calculate_accuracy_sim(extracted_index_sim_p3m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p3", "m2", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p3m2 <- valid_reps(parent_dir) 
enum_table_sim_p3m2 <- calculate_accuracy_sim(extracted_index_sim_p3m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p3", "m3", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p3m3 <- valid_reps(parent_dir) 
enum_table_sim_p3m3 <- calculate_accuracy_sim(extracted_index_sim_p3m3) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p4", "m1", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p4m1 <- valid_reps(parent_dir) 
enum_table_sim_p4m1 <- calculate_accuracy_sim(extracted_index_sim_p4m1) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p4", "m2", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p4m2 <- valid_reps(parent_dir) 
enum_table_sim_p4m2 <- calculate_accuracy_sim(extracted_index_sim_p4m2) 

# Define the parent directory containing all folders
parent_dir <- here("enumeration", "simple", "p4", "m3", "ideal")
# Extracted summary of all replications across folders
extracted_index_sim_p4m3 <- valid_reps(parent_dir) 
enum_table_sim_p4m3 <- calculate_accuracy_sim(extracted_index_sim_p4m3) 
```


```{r, eval = FALSE, include= FALSE}
# Save files
total_sim1 <- as.data.frame(rbind(enum_table_sim_p1m1$combined_percentages, 
                                  enum_table_sim_p2m1$combined_percentages, 
                                  enum_table_sim_p2m2$combined_percentages)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 
total_sim2 <- as.data.frame(rbind(enum_table_sim_p3m1$combined_percentages, 
                                  enum_table_sim_p3m2$combined_percentages, 
                                  enum_table_sim_p3m3$combined_percentages,
                                  enum_table_sim_p4m1$combined_percentages, 
                                  enum_table_sim_p4m2$combined_percentages, 
                                  enum_table_sim_p4m3$combined_percentages))%>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(total_sim1, here("tables", "ideal_sim1.csv"))
#write_csv(total_sim2, here("tables", "ideal_sim2.csv"))
```

*Note*: The last column in VLMR is NA, which indicates no nonsignificant p-value was found for that condition across replications.

```{r}
source(here("functions","process_enum"))
total_sim1 <- read_csv(here("tables", "ideal_sim1.csv")) %>% 
  select(-sim_model) 

total_sim2 <- read_csv(here("tables", "ideal_sim2.csv")) %>% 
  select(-sim_model) %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))


table_sim1 <- gt_table_sim(total_sim1)
table_sim2 <- gt_table_sim(total_sim2)

table_sim1
table_sim2

#gtsave(table_sim1, here("tables", "table_sim1.docx"))
#gtsave(table_sim2, here("tables", "table_sim2.docx"))
```

# Entropy

## Realistic

### Complex

Entropy averaged across replications for true class only.

```{r,  eval = FALSE, include= FALSE}
source(here("functions","extract_entropy"))

# P1 M1
parent_dir <- here("enumeration", "complex", "p1", "m1", "realistic")
entropy_com_p1m1 <- extract_entropy(parent_dir)

# P2 M1
parent_dir <- here("enumeration", "complex", "p2", "m1", "realistic")
entropy_com_p2m1 <- extract_entropy(parent_dir)

# P2 M2
parent_dir <- here("enumeration", "complex", "p2", "m2", "realistic")
entropy_com_p2m2 <- extract_entropy(parent_dir)

# P3 M1
parent_dir <- here("enumeration", "complex", "p3", "m1", "realistic")
entropy_com_p3m1 <- extract_entropy(parent_dir)

# P3 M2
parent_dir <- here("enumeration", "complex", "p3", "m2", "realistic")
entropy_com_p3m2 <- extract_entropy(parent_dir)

# P3 M3
parent_dir <- here("enumeration", "complex", "p3", "m3", "realistic")
entropy_com_p3m3 <- extract_entropy(parent_dir)

# P4 M1
parent_dir <- here("enumeration", "complex", "p4", "m1", "realistic")
entropy_com_p4m1 <- extract_entropy(parent_dir)

# P4 M2
parent_dir <- here("enumeration", "complex", "p4", "m2", "realistic")
entropy_com_p4m2 <- extract_entropy(parent_dir)

# P4 M3
parent_dir <- here("enumeration", "complex", "p4", "m3", "realistic")
entropy_com_p4m3 <- extract_entropy(parent_dir)
```

```{r, eval = FALSE, include= FALSE}
# Save files
entropy_com1 <- as.data.frame(rbind(entropy_com_p1m1, entropy_com_p2m1, entropy_com_p2m2))  %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

entropy_com2 <- as.data.frame(rbind(entropy_com_p3m1, 
                                  entropy_com_p3m2, 
                                  entropy_com_p3m3,
                                  entropy_com_p4m1, 
                                  entropy_com_p4m2, 
                                  entropy_com_p4m3)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(entropy_com1, here("tables", "entropy_real_com1.csv"))
#write_csv(entropy_com2, here("tables", "entropy_real_com2.csv"))
```


```{r}
entropy_com1 <- read_csv(here("tables", "entropy_real_com1.csv")) %>% 
  select(-sim_model)

entropy_com2 <- read_csv(here("tables", "entropy_real_com2.csv")) %>% 
  select(-sim_model)

summary(entropy_com1$entropy)
summary(entropy_com2$entropy)

```

### Simple

Entropy averaged across replications for true class only.

```{r,  eval = FALSE, include= FALSE}
source(here("functions","extract_entropy"))

# P1 M1
parent_dir <- here("enumeration", "simple", "p1", "m1", "realistic")
entropy_sim_p1m1 <- extract_entropy(parent_dir)

# P2 M1
parent_dir <- here("enumeration", "simple", "p2", "m1", "realistic")
entropy_sim_p2m1 <- extract_entropy(parent_dir)

# P2 M2
parent_dir <- here("enumeration", "simple", "p2", "m2", "realistic")
entropy_sim_p2m2 <- extract_entropy(parent_dir)

# P3 M1
parent_dir <- here("enumeration", "simple", "p3", "m1", "realistic")
entropy_sim_p3m1 <- extract_entropy(parent_dir)

# P3 M2
parent_dir <- here("enumeration", "simple", "p3", "m2", "realistic")
entropy_sim_p3m2 <- extract_entropy(parent_dir)

# P3 M3
parent_dir <- here("enumeration", "simple", "p3", "m3", "realistic")
entropy_sim_p3m3 <- extract_entropy(parent_dir)

# P4 M1
parent_dir <- here("enumeration", "simple", "p4", "m1", "realistic")
entropy_sim_p4m1 <- extract_entropy(parent_dir)

# P4 M2
parent_dir <- here("enumeration", "simple", "p4", "m2", "realistic")
entropy_sim_p4m2 <- extract_entropy(parent_dir)

# P4 M3
parent_dir <- here("enumeration", "simple", "p4", "m3", "realistic")
entropy_sim_p4m3 <- extract_entropy(parent_dir)
```

```{r, eval = FALSE, include= FALSE}
# Save files
entropy_sim1 <- as.data.frame(rbind(entropy_sim_p1m1, entropy_sim_p2m1, entropy_sim_p2m2))  %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

entropy_sim2 <- as.data.frame(rbind(entropy_sim_p3m1, 
                                  entropy_sim_p3m2, 
                                  entropy_sim_p3m3,
                                  entropy_sim_p4m1, 
                                  entropy_sim_p4m2, 
                                  entropy_sim_p4m3)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(entropy_sim1, here("tables", "entropy_real_sim1.csv"))
#write_csv(entropy_sim2, here("tables", "entropy_real_sim2.csv"))
```

```{r}
entropy_sim1 <- read_csv(here("tables", "entropy_real_sim1.csv")) %>% 
  select(-sim_model)

entropy_sim2 <- read_csv(here("tables", "entropy_real_sim2.csv")) %>% 
  select(-sim_model)

summary(entropy_sim1$entropy)
summary(entropy_sim2$entropy)

```

## Ideal

### Complex

Entropy averaged across replications for true class only.

```{r, eval = FALSE, include= FALSE}
source(here("functions","extract_entropy"))

# P1 M1
parent_dir <- here("enumeration", "complex", "p1", "m1", "ideal")
entropy_com_p1m1 <- extract_entropy(parent_dir)

# P2 M1
parent_dir <- here("enumeration", "complex", "p2", "m1", "ideal")
entropy_com_p2m1 <- extract_entropy(parent_dir)

# P2 M2
parent_dir <- here("enumeration", "complex", "p2", "m2", "ideal")
entropy_com_p2m2 <- extract_entropy(parent_dir)

# P3 M1
parent_dir <- here("enumeration", "complex", "p3", "m1", "ideal")
entropy_com_p3m1 <- extract_entropy(parent_dir)

# P3 M2
parent_dir <- here("enumeration", "complex", "p3", "m2", "ideal")
entropy_com_p3m2 <- extract_entropy(parent_dir)

# P3 M3
parent_dir <- here("enumeration", "complex", "p3", "m3", "ideal")
entropy_com_p3m3 <- extract_entropy(parent_dir)

# P4 M1
parent_dir <- here("enumeration", "complex", "p4", "m1", "ideal")
entropy_com_p4m1 <- extract_entropy(parent_dir)

# P4 M2
parent_dir <- here("enumeration", "complex", "p4", "m2", "ideal")
entropy_com_p4m2 <- extract_entropy(parent_dir)

# P4 M3
parent_dir <- here("enumeration", "complex", "p4", "m3", "ideal")
entropy_com_p4m3 <- extract_entropy(parent_dir)
```

```{r, eval = FALSE, include= FALSE}
# Save files
entropy_com1 <- as.data.frame(rbind(entropy_com_p1m1, entropy_com_p2m1, entropy_com_p2m2))  %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

entropy_com2 <- as.data.frame(rbind(entropy_com_p3m1, 
                                  entropy_com_p3m2, 
                                  entropy_com_p3m3,
                                  entropy_com_p4m1, 
                                  entropy_com_p4m2, 
                                  entropy_com_p4m3)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(entropy_com1, here("tables", "entropy_ideal_com1.csv"))
#write_csv(entropy_com2, here("tables", "entropy_ideal_com2.csv"))
```

```{r}
entropy_com1 <- read_csv(here("tables", "entropy_ideal_com1.csv")) %>% 
  select(-sim_model)

entropy_com2 <- read_csv(here("tables", "entropy_ideal_com2.csv")) %>% 
  select(-sim_model)

summary(entropy_com1$entropy)
summary(entropy_com2$entropy)

```

### Simple

Entropy averaged across replications for true class only.

```{r, eval = FALSE, include= FALSE}
source(here("functions","extract_entropy"))

# P1 M1
parent_dir <- here("enumeration", "simple", "p1", "m1", "ideal")
entropy_sim_p1m1 <- extract_entropy(parent_dir)

# P2 M1
parent_dir <- here("enumeration", "simple", "p2", "m1", "ideal")
entropy_sim_p2m1 <- extract_entropy(parent_dir)

# P2 M2
parent_dir <- here("enumeration", "simple", "p2", "m2", "ideal")
entropy_sim_p2m2 <- extract_entropy(parent_dir)

# P3 M1
parent_dir <- here("enumeration", "simple", "p3", "m1", "ideal")
entropy_sim_p3m1 <- extract_entropy(parent_dir)

# P3 M2
parent_dir <- here("enumeration", "simple", "p3", "m2", "ideal")
entropy_sim_p3m2 <- extract_entropy(parent_dir)

# P3 M3
parent_dir <- here("enumeration", "simple", "p3", "m3", "ideal")
entropy_sim_p3m3 <- extract_entropy(parent_dir)

# P4 M1
parent_dir <- here("enumeration", "simple", "p4", "m1", "ideal")
entropy_sim_p4m1 <- extract_entropy(parent_dir)

# P4 M2
parent_dir <- here("enumeration", "simple", "p4", "m2", "ideal")
entropy_sim_p4m2 <- extract_entropy(parent_dir)

# P4 M3
parent_dir <- here("enumeration", "simple", "p4", "m3", "ideal")
entropy_sim_p4m3 <- extract_entropy(parent_dir)
```

```{r, eval = FALSE, include= FALSE}
# Save files
entropy_sim1 <- as.data.frame(rbind(entropy_sim_p1m1, entropy_sim_p2m1, entropy_sim_p2m2))  %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 

entropy_sim2 <- as.data.frame(rbind(entropy_sim_p3m1, 
                                  entropy_sim_p3m2, 
                                  entropy_sim_p3m3,
                                  entropy_sim_p4m1, 
                                  entropy_sim_p4m2, 
                                  entropy_sim_p4m3)) %>% 
  mutate(
    p = sub("(p\\d)m\\d", "\\1", sim_model), 
    m = sub("p\\dm(\\d)", "m\\1", sim_model)  
  ) 


#write_csv(entropy_sim1, here("tables", "entropy_ideal_sim1.csv"))
#write_csv(entropy_sim2, here("tables", "entropy_ideal_sim2.csv"))
```

```{r}
entropy_sim1 <- read_csv(here("tables", "entropy_ideal_sim1.csv")) %>% 
  select(-sim_model)

entropy_sim2 <- read_csv(here("tables", "entropy_ideal_sim2.csv")) %>% 
  select(-sim_model)

summary(entropy_sim1$entropy)
summary(entropy_sim2$entropy)

```

## Total Entropy 

```{r}
ideal_com1 <- read_csv(here("tables", "entropy_ideal_com1.csv")) %>% 
  filter(k == 5)
ideal_com2 <- read_csv(here("tables", "entropy_ideal_com2.csv"))%>% 
  filter(k == 5)
ideal_sim1 <- read_csv(here("tables", "entropy_ideal_sim1.csv"))%>% 
  filter(k == 4)
ideal_sim2 <- read_csv(here("tables", "entropy_ideal_sim2.csv"))%>% 
  filter(k == 4)

real_com1 <- read_csv(here("tables", "entropy_real_com1.csv"))%>% 
  filter(k == 5)
real_com2 <- read_csv(here("tables", "entropy_real_com2.csv"))%>% 
  filter(k == 5)
real_sim1 <- read_csv(here("tables", "entropy_real_sim1.csv"))%>% 
  filter(k == 4)
real_sim2 <- read_csv(here("tables", "entropy_real_sim2.csv"))%>% 
  filter(k == 4)

entropy_ideal <- rbind(ideal_com1, ideal_sim1) %>% 
  mutate(de = NA) %>% 
  rbind(ideal_com2, ideal_sim2) %>% 
  mutate(entropy = as.numeric(entropy)) 

entropy_real <- rbind(real_com1, real_sim1) %>% 
  mutate(de = NA) %>% 
  rbind(real_com2, real_sim2) %>% 
  mutate(entropy = as.numeric(entropy))

summary(entropy_ideal$entropy)
summary(entropy_real$entropy)
```

# ANOVA Analyses

Read in data

```{r}
ideal_com1 <- read_csv(here("tables", "ideal_com1.csv"))
ideal_com2 <- read_csv(here("tables", "ideal_com2.csv"))
ideal_sim1 <- read_csv(here("tables", "ideal_sim1.csv"))
ideal_sim2 <- read_csv(here("tables", "ideal_sim2.csv"))

real_com1 <- read_csv(here("tables", "real_com1.csv"))
real_com2 <- read_csv(here("tables", "real_com2.csv"))
real_sim1 <- read_csv(here("tables", "real_sim1.csv"))
real_sim2 <- read_csv(here("tables", "real_sim2.csv"))

anova_com <- rbind(ideal_com1, real_com1) %>% 
  mutate(de = NA) %>% 
  rbind(ideal_com2, real_com2) %>% 
  select(Fit_Index:model, de, Class_5, p, m) %>% 
  mutate(prop_correct = Class_5 / 100,
         de = factor(de),
         N = factor(N)) %>% 
  rename(correct_class = Class_5) 

anova_sim <- rbind(ideal_sim1, real_sim1) %>% 
  mutate(de = NA) %>% 
  rbind(ideal_sim2, real_sim2) %>% 
  select(Fit_Index:model, de, Class_4, p, m) %>% 
  mutate(prop_correct = Class_4 / 100,
         de = factor(de),
         N = factor(N)) %>% 
  rename(correct_class = Class_4)

total_anova <- rbind(anova_com, anova_sim) %>% 
  rename(fit_index = Fit_Index) %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))
```

ANOVA Results

## Full 

With DE

```{r}
options(max.print = 2000)

# ANOVA results
anova_result <- aov(prop_correct ~ de + p + m + N + model + k_split + separation + fit_index,
                    data = total_anova)
summary(anova_result)
tukey <- TukeyHSD(anova_result)
tukey
#plot(tukey, las = 1)
eta_squared(anova_result)
#plot(anova_result, which = 2)

#apa.aov.table(anova_result,
#              filename = here("tables", "anova_table.doc"),
#              table.number = 1)
```

Without DE

```{r}
options(max.print = 2000)

# ANOVA results
anova_result <- aov(prop_correct ~  p + m + N + model + k_split + separation + fit_index,
                    data = total_anova)
summary(anova_result)
TukeyHSD(anova_result)
eta_squared(anova_result)
```

## Interactions

```{r}
options(max.print = 2000)

anova_result <- aov(
  prop_correct ~ N * fit_index + de * fit_index + p * fit_index + m * fit_index + model *
    fit_index + k_split * fit_index + separation * fit_index +
    de + p + m + N + model + k_split + separation + fit_index,
  data = total_anova
)
summary(anova_result)
#TukeyHSD(anova_result)
eta_squared(anova_result)
```

## BIC Only

```{r}
options(max.print = 2000) 

# ANOVA results
total_BIC <- total_anova %>% 
  filter(fit_index == "BIC")
anova_result <- aov(prop_correct ~ de + p + m + N + model + k_split + separation, data = total_BIC)
summary(anova_result)
TukeyHSD(anova_result)
eta_squared(anova_result)
```


```{r, eval = FALSE, include = FALSE}
tukey_df <- tidy(tukey, conf.int = TRUE)

tukey_table <- tukey_df %>%
  mutate(
    p_value = case_when(
      adj.p.value < .001 ~ "< .001",
      TRUE ~ sprintf("%.3f", adj.p.value)
    ),
    CI = sprintf("[%.2f, %.2f]", conf.low, conf.high)  # Format CI
  ) %>% 
  select(-null.value) %>% 
  gt() %>%
  tab_header(title = "Tukey HSD Post Hoc Test Results") %>%
  fmt_number(
    columns = c(estimate, conf.low, conf.high, adj.p.value),
    decimals = 3
  ) %>%
  cols_label(
    term = "Term",
    contrast = "Comparison",
    estimate = "Difference",
    conf.low = "Lower CI",
    conf.high = "Upper CI",
    adj.p.value = "p-value"
  )
tukey_table

#gtsave(tukey_table, here("tables", "tukey.docx"))
```


# Over/Underextraction

Underextraction was computed as the sum of all solutions selecting fewer classes than the true model minus the percentage selecting the correct number of classes, while overextraction was calculated as the percentage selecting more classes than the true model minus the correct class percentage.

```{r}
extract_com <- rbind(ideal_com1, real_com1) %>% 
  mutate(de = NA) %>% 
  rbind(ideal_com2, real_com2) %>% 
  mutate(prop_correct = Class_5 / 100,
         de = factor(de),
         N = factor(N)) %>%
  rowwise() %>% 
  mutate(under_ext = sum(c_across(Class_2:Class_4), na.rm = T)-Class_5,
         over_ext = Class_6-Class_5) %>% 
  ungroup() %>% 
  rename(correct_class = Class_5) %>% 
  select(Fit_Index, N, k_split, separation, model, p, m, de, under_ext, over_ext, correct_class) 

extract_sim <- rbind(ideal_sim1, real_sim1) %>% 
  mutate(de = NA) %>% 
  rbind(ideal_sim2, real_sim2) %>% 
  mutate(prop_correct = Class_4 / 100,
         de = factor(de),
         N = factor(N)) %>% 
  rowwise() %>% 
  mutate(under_ext = sum(c_across(Class_2:Class_3), na.rm = T)-Class_4,
         over_ext = Class_5-Class_4) %>% 
  ungroup() %>% 
  rename(correct_class = Class_4) %>% 
  select(Fit_Index, N, k_split, separation, model, p, m, de, under_ext, over_ext, correct_class) 

full_extract <- extract_com %>% 
  full_join(extract_sim) %>% 
  arrange(correct_class) %>% 
  filter(Fit_Index != "cmPk")


under_ext <- full_extract %>%
  filter(under_ext > 0) %>% 
  arrange(desc(under_ext))

over_ext <- full_extract %>%
  filter(over_ext > 0) %>% 
  arrange(desc(over_ext)) %>% 
  filter(Fit_Index != "VLMR")
```

## Underextraction 

### For each condition

```{r}
# Underextraction for each condition, separately
under_ext %>%
  select(Fit_Index) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "level") %>%
  group_by(variable, level) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(variable, desc(count)) %>% 
  arrange(desc(count))
```


### Model Selection Criterion x N

```{r}
under_ext %>%
  count(Fit_Index, separation) %>% 
  arrange(desc(n))
```

### Model Selection Criterion x Analysis model

```{r}
under_ext %>%
  count(Fit_Index, m) %>% 
  arrange(desc(n))
```

### Model Selection Criterion x Analysis model x DE

```{r}
under_ext %>%
  count(Fit_Index, m, de) %>% 
  #filter(Fit_Index != "AWE") %>% 
  arrange(desc(n))
```

### Model Selection Criterion x Analysis model x N

```{r}
under_ext %>%
  count(Fit_Index, m, N) %>% 
  filter(Fit_Index != "AWE") %>% 
  arrange(desc(n))
```


## Overextraction 

### For each condition, separately

```{r}
over_ext %>%
  select(Fit_Index) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "level") %>%
  group_by(variable, level) %>%
  summarise(count = n(), .groups = "drop") %>%
  arrange(variable, desc(count)) %>% 
  arrange(desc(count))
```


### Model Selection Criterion x N

```{r}
over_ext %>%
  count(Fit_Index, N) %>% 
  arrange(desc(n))
```


### Model Selection Criterion x Analysis model

```{r}
over_ext %>%
  count(Fit_Index, m) %>% 
  arrange(desc(n))
```

### Model Selection Criterion x Analysis model x DE

```{r}
over_ext %>%
  count(Fit_Index, m, de) %>% 
  arrange(desc(n))
```

### Model Selection Criterion x Analysis model x N

```{r}
over_ext %>%
  count(Fit_Index, m, N) %>% 
  arrange(desc(n))
```


## BIC Only

```{r}
over_ext_bic <- over_ext %>% 
  filter(Fit_Index == "BIC")

under_ext_bic <- under_ext %>% 
  filter(Fit_Index == "BIC")
```


#### Underextraction

##### Analysis model x N

```{r}
under_ext_bic %>%
  count(m, p, de) %>% 
  arrange(desc(n))
```

#### Overextraction

##### Analysis model x N

```{r}
over_ext_bic %>%
  count(m, p, de) %>% 
  arrange(desc(n))
```


# Manuscript Plots

Data 

```{r}
plot_data <- total_anova %>% 
  filter(fit_index != "cmPk") %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))

BIC_only <- plot_data %>% 
  filter(fit_index == "BIC") %>% 
  mutate(p = case_when(
    p == "p3" ~ "p3a",
    p == "p4" ~ "p3b",
    TRUE ~ p
  ))
```

APA colors

```{r}
# Define APA-appropriate color palette (muted colors)
apa_colors_2 <- c("#1b9e77",  # Teal
  "#d95f02",  # Orange
  "#7a5195",  # Purple
  "#ef5675",  # Coral
  "#66a61e",  # Green
  "#ffa600",  # Yellow
  "#2f4b7c",  # Teal
  "#666666")  # Gray


apa_colors <- c(
  "aBIC" = "#1b9e77",
  "AWE" = "#d95f02",
  "BIC" = "#7570b3",
  "CAIC" = "#e7298a",
  "VLMR" = "#66a61e",
  "cmPk" = "#e6ab02"  # Add 6th color if needed
)
```

## Interaction Plots

```{r}
# Interaction Line Plots

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$de, 
                 response = plot_data$prop_correct, col = rainbow(3),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$k_split, 
                 response = plot_data$prop_correct, col = rainbow(2),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$sim_model, 
                 response = plot_data$prop_correct, col = rainbow(9),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$model, 
                 response = plot_data$prop_correct, col = rainbow(2),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$p, 
                 response = plot_data$prop_correct, col = rainbow(4),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$m, 
                 response = plot_data$prop_correct, col = rainbow(3),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")

interaction.plot(x.factor = plot_data$N, trace.factor = plot_data$fit_index, 
                 response = plot_data$prop_correct, col = rainbow(3),
                 lty = 1, xlab = "Sample Size", ylab = "Proportion Correctly Identified")
```

## Single *Condition* Barplots

```{r}
# Model Selection Criterion
fit_bar <- plot_data %>% 
  ggplot(aes(x = fct_reorder(fit_index, prop_correct, .fun = mean, .desc = TRUE), y = prop_correct, fill = as.factor(fit_index))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Model Selection Criterion",
       x = "Model Selection Criterion",
       y = "Average Recovery Rate") +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(plot_data$fit_index)))) + # Fix color mapping
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
fit_bar
ggsave(here("figures", "fit_bar.jpeg"), dpi="retina", height = 3, width = 5, bg = "white",  units="in")


# Sample Size
N_bar <- BIC_only %>% 
  ggplot(aes(x = N, 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 3,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Sample Size",
       x = "Sample Size",
       y = "Average Recovery Rate") +
 #scale_fill_manual(values = rep("#d95f02", length(unique(plot_data$fit_index))))+
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[1],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
N_bar
ggsave(here("figures", "N_bar.jpeg"), height = 3, width = 5, dpi="retina", bg = "white",  units="in")


# Population 
p_bar <- BIC_only %>% 
  mutate(p = toTitleCase(p)) %>% 
  ggplot(aes(x = p, 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Population Model",
       x = "Population Model",
       y = "Average Recovery Rate") +
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[2],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
p_bar
ggsave(here("figures", "p_bar.jpeg"), height = 3, width = 5, dpi="retina", bg = "white",  units="in")



# Analysis Model 
m_bar <- BIC_only %>% 
  mutate(m = toTitleCase(m)) %>% 
  ggplot(aes(x = m, 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Analysis Model",
       x = "Analysis Model",
       y = "Average Recovery Rate") +
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[3],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
m_bar
ggsave(here("figures", "m_bar.jpeg"), height = 3, width = 5, dpi="retina", bg = "white",  units="in")



# DE  Model 
de_bar <- BIC_only %>% 
  filter(de != "NA") %>% 
 # mutate(de = fct_explicit_na(de, na_level = "NA"),  
#         de = fct_relevel(de, "NA", "0.405", "0.9", "1.5"))  %>% 
  ggplot(aes(x = fct_reorder(de, prop_correct, .fun = mean, .desc = TRUE), 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Direct Effect",
       x = "Direct Effect",
       y = "Average Recovery Rate") +
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[4],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
de_bar
ggsave(here("figures", "de_bar.jpeg"), height = 3, width = 5, dpi="retina", bg = "white",  units="in")



# K split  Model 
k_bar <- BIC_only %>% 
  mutate(k_split = toTitleCase(k_split)) %>% 
  ggplot(aes(x = fct_reorder(k_split, prop_correct, .fun = mean, .desc = TRUE), 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Class Proportion",
       x = "Class Proportion",
       y = "Average Recovery Rate") +
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[5],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
k_bar
ggsave(here("figures", "k_bar.jpeg"), dpi="retina", height = 3, width = 5, bg = "white",  units="in")



# Separation
sep_bar <- BIC_only %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  ggplot(aes(x = fct_reorder(separation, prop_correct, .fun = mean, .desc = TRUE), 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Separation",
       x = "Separation",
       y = "Average Recovery Rate") +
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[6],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
sep_bar
ggsave(here("figures", "sep_bar.jpeg"), dpi="retina", height = 3, width = 5, bg = "white",  units="in")



# Measurement model
model_bar <- BIC_only %>% 
  mutate(model = toTitleCase(model)) %>% 
  ggplot(aes(x = fct_reorder(model, prop_correct, .fun = mean, .desc = TRUE), 
             y = prop_correct,
             fill = after_stat(y))) +  # Fill based on bar height
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(
    fun = mean,
    geom = "text",
    aes(label = format(..y.., digits = 2, nsmall = 2)),
    position = position_dodge(0.9),
    vjust = 4,
    size = 5,
    family = "serif",
    color = "black"
  ) +
  labs(title = "Average Recovery Rate by Measurement Model",
       x = "Measurement Model",
       y = "Average Recovery Rate") +
  scale_fill_gradient(
    low = "white", 
    high = apa_colors_2[7],       # APA-style green
    limits = c(0, 1),       # Ensure 0 maps to white
    oob = scales::squish     # Keeps out-of-bound values in range
  ) +
  ylim(0, 1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.position = "none"  # Remove legend
  )
model_bar
ggsave(here("figures", "model_bar.jpeg"), dpi="retina", height = 3, width = 5, bg = "white",  units="in")
```

Combine:

```{r}
no_y_axis <- theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

combined_plot <- (
  p_bar + labs(title = NULL) |
    m_bar  + labs(title = NULL) + no_y_axis |
    N_bar + labs(title = NULL) + no_y_axis
) /
  (
    sep_bar + labs(title = NULL) |
      de_bar + labs(title = NULL) + no_y_axis |
      k_bar + labs(title = NULL) + no_y_axis |
      model_bar + labs(title = NULL) + no_y_axis
  ) +
  plot_layout(guides = "collect") +
  plot_annotation(title = "Average Recovery Rates Across Study Conditions for BIC Only", tag_levels = "A") +
  theme(
    text = element_text(
      family = "serif",
      size = 16,
      color = "black"
    ),
    plot.title = element_text(
      size = 14,
      color = "black",
      face = "bold",
      hjust = 0.5
    ),
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 12, color = "black"),
    strip.text = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 11),
    legend.position = "none"
  )
combined_plot
ggsave(here("figures", "N_fit_bar_combined.jpeg"), height = 7, width = 12, dpi="retina", bg = "white",  units="in")
```


## N x *Condition* Barplots

```{r}

# Model Selection Criterion
plot_data %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(fit_index))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Model Selection Criterion and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Model Selection Criterion") +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(plot_data$fit_index)-1))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "fit_N_bar.jpeg"), dpi="retina", bg = "white",  units="in")

# Population Models
plot_data %>% 
  mutate(p = toTitleCase(p)) %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(p))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Population Model and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Population Model") +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(toTitleCase(plot_data$p))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "p_N_bar.jpeg"), dpi="retina", bg = "white", units="in")

# Analysis Model
analysis_model_colors <- c(
  "M1" = "#d4b9da",  # light lavender
  "M2" = "#b39fc8",  # medium purple
  "M3" = "#7a5195"   # deep APA purple
)
BIC_only %>% 
  mutate(m = toTitleCase(m)) %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(m))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(fun = mean,
             geom = "text",
             aes(label = format(..y.., digits = 2, nsmall = 2)),
             position = position_dodge(0.9),
             vjust = 3,
             size = 4,
             family = "serif",
             color = "black") +
  labs(title = "Average Recovery Rate by Analysis Model and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Analysis Model") +
  scale_fill_manual(values = setNames(analysis_model_colors, levels(as.factor(toTitleCase(BIC_only$m))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "m_N_bar1.jpeg"), height =4, width = 6, dpi="retina", bg = "white", units="in")

# Analsis Model 2
BIC_only %>% 
  mutate(m = toTitleCase(m)) %>% 
  ggplot(aes(x = m, y = prop_correct, fill = as.factor(N))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Sample Size and Analysis Model",
       x = "Analysis Model",
       y = "Average Recovery Rate",
       fill = "Sample Size") +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(BIC_only$N)))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "m_N_bar2.jpeg"), height =4, width = 5, dpi="retina", bg = "white", units="in")

de_colors <- c(
  #"NA" = "white",
  "0.405" = "#fddde0",  # light coral pink
  "0.9"   = "#f98b9b",  # medium coral
  "1.5"   = "#ef5675"   # deep coral pink (your original)
)
# DE
BIC_only %>% 
  filter(!is.na(de)) %>%  # Corrected filtering of NA values
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(de))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(fun = mean,
             geom = "text",
             aes(label = format(..y.., digits = 2, nsmall = 2)),
             position = position_dodge(0.9),
             vjust = 3,
             size = 4,
             family = "serif",
             color = "black") +
  labs(title = "Average Recovery Rate by DE and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Direct Effects") +
  scale_fill_manual(values = setNames(de_colors, levels(as.factor(BIC_only$de)))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
ggsave(here("figures", "de_N_bar.jpeg"), height =4, width =6,  dpi="retina", bg = "white", units="in")

# Class Proportion
plot_data %>% 
  mutate(k_split = toTitleCase(k_split)) %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(k_split))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Class Proportion and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Class Proportion") +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(toTitleCase(plot_data$k_split))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "k_N_bar.jpeg"), dpi="retina", bg = "white", units="in")

separation_colors <- c(
  "Low"  = "#ffdf99",  # Light golden yellow (soft, pastel-like)
  "High" = "#ffa600"   # Vibrant golden orange (your original)
)
# Separation
BIC_only %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  stat_summary(fun = mean,
             geom = "text",
             aes(label = format(..y.., digits = 2, nsmall = 2)),
             position = position_dodge(0.9),
             vjust = 3,
             size = 5,
             family = "serif",
             color = "black") +
  labs(title = "Average Recovery Rate by Separation and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(separation_colors, levels(as.factor(toTitleCase(BIC_only$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "sep_N_bar.jpeg"), dpi="retina", height =4, width = 6,  bg = "white", units="in")


# Measurement Model
plot_data %>% 
  mutate(model = toTitleCase(model)) %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(model))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Measurement Model and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Measurement Model") +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(toTitleCase(plot_data$model))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "model_N_bar.jpeg"), dpi="retina", bg = "white", units="in")
```

## Fit x *Condition* Lineplot

```{r, fig.height=5, fig.width=7}
fit_plot_data <- plot_data %>%
  mutate(fit_index = fct_relevel(fit_index, "BIC", "CAIC", "aBIC", "VLMR", "AWE"))
# Sample Size
fit_n_line <- fit_plot_data %>% 
  group_by(N, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = N, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(linewidth = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Sample Size", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Sample Size and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_n_line
ggsave(here("figures", "n_fit_int.jpeg"), dpi="retina", bg = "white", height=4, width=5, units="in")

# Population Model
fit_p_line <- fit_plot_data %>% 
  mutate(p = toTitleCase(p)) %>% 
  group_by(p, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = p, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Population Model", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Population Model and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_p_line
ggsave(here("figures", "p_fit_int.jpeg"), dpi="retina", bg = "white", height=4, width=5, units="in")

# Analysis Model 
fit_m_line <- fit_plot_data %>% 
  mutate(m = toTitleCase(m)) %>% 
  group_by(m, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = m, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Analysis Model", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rate by Analysis Model and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_m_line
ggsave(here("figures", "m_fit_int.jpeg"), dpi="retina", bg = "white", height=4, width=5, units="in")

# Direct Effect
fit_de_line<- fit_plot_data %>%
  filter(!is.na(de)) %>%  # Corrected filtering of NA values
  mutate(de = fct_explicit_na(de, na_level = "NA"),  
         de = fct_relevel(de, "0.405", "0.9", "1.5"))  %>% 
  rename(`Split` = k_split,
         `DE` = de) %>% 
  group_by(`DE`, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = `DE`, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Direct Effect", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Direct Effect and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_de_line
ggsave(here("figures", "de_fit_int.jpeg"), dpi="retina", bg = "white", height=5, width=7, units="in")

# Class Proportion
fit_k_line <- fit_plot_data %>% 
  rename(`Split` = k_split,
         `DE` = de) %>% 
  mutate(`Split` = toTitleCase(`Split`)) %>% 
  group_by(`Split`, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = `Split`, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Class Proportion", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Class Proportion and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_k_line
ggsave(here("figures", "k_fit_int.jpeg"), dpi="retina", bg = "white", height=4, width=5, units="in")

# Separation
fit_sep_line <- fit_plot_data %>% 
  rename(`Separation` = separation,
         `DE` = de) %>% 
  mutate(`Separation` = toTitleCase(`Separation`)) %>% 
  group_by(`Separation`, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = `Separation`, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Separation", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Separation and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_sep_line
ggsave(here("figures", "sep_fit_int.jpeg"), dpi="retina", bg = "white", height=4, width=5, units="in")


# Measurement
fit_model_line <- fit_plot_data %>% 
  rename(`Measurement Model` = model,
         `DE` = de) %>% 
  mutate(`Measurement Model` = toTitleCase(`Measurement Model`)) %>% 
  group_by(`Measurement Model`, fit_index) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
ggplot(aes(x = `Measurement Model`, y = mean_prop_correct, group = fit_index, color = fit_index)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Measurement Model", 
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Measurement Model and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
fit_model_line
ggsave(here("figures", "model_fit_int.jpeg"), dpi="retina", bg = "white", height=4, width=5, units="in")
```


Combine:

```{r}
no_y_axis <- theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

combined_plot <- (
  fit_p_line + labs(title = NULL) |
    fit_m_line  + labs(title = NULL) + no_y_axis |
    fit_n_line + labs(title = NULL) + no_y_axis
) /
  (
    fit_sep_line + labs(title = NULL) |
      fit_de_line + labs(title = NULL) + no_y_axis |
      fit_k_line + labs(title = NULL) + no_y_axis |
      fit_model_line + labs(title = NULL) + no_y_axis
  ) +
  plot_layout(guides = "collect") +
  plot_annotation(title = "Average Recovery Rates Across Model Selection Criterion and Study Conditions", tag_levels = "A") +
  theme(
    text = element_text(
      family = "serif",
      size = 16,
      color = "black"
    ),
    # APA requires serif font
    plot.title = element_text(
      size = 14,
      color = "black",
      face = "bold",
      hjust = 0.5
    ),
    # Center-align title
    axis.title = element_text(size = 12, face = "bold"),
    axis.text = element_text(size = 12, color = "black"),
    strip.text = element_text(size = 12, face = "bold"),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 11),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )
combined_plot
ggsave(here("figures", "fit_lineplots_combined.jpeg"), height = 7, width = 12, dpi="retina", bg = "white",  units="in")

```


## Fit x N x *Condition* Lineplot

```{r, fig.width = 12, fig.height= 9}

# All Sim Models
plot_data %>% 
  mutate(sim_model = toupper(sim_model)) %>% 
  group_by(N, fit_index, sim_model) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = N, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~sim_model, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Sample Size (N)",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Sample Size and Simulation Models"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
ggsave(here("figures", "p1234_m123_N_fit.jpeg"), dpi="retina", bg = "white", height=7, width=9, units="in")

# P34 x M123
fit_plot_data %>% 
  filter(sim_model != "p1m1",
         sim_model != "p2m1",
         sim_model != "p2m2") %>%  
  mutate(m = toTitleCase(m),
         p = toTitleCase(p)) %>% 
  rename(`Split` = k_split,
         `DE` = de) %>% 
  group_by(m, fit_index, N) %>% 
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ggplot(aes(x = N, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_grid(~ m, labeller = label_value) +
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Sample Size (N)",
    y = "Average Recovery Rate",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Sample Size, Analysis Model, and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "m123_N_fit.jpeg"), dpi="retina", bg = "white", height=4, width=8, units="in")

# DE
plot_data %>% 
  group_by(N, fit_index, de) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  #mutate(de = fct_explicit_na(de, na_level = "NA"),  
  #       de = fct_relevel(de, "NA", "0.405", "0.9", "1.5"))  %>% 
  ggplot(aes(x = N, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~de, labeller = labeller(de = function(x) paste("Direct Effects:", x))) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Sample Size (N)",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Sample Size and Direct Effects"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "de_N_fit.jpeg"), dpi="retina", bg = "white", height=5, width=9, units="in")


# DE X M X Fit
fit_plot_data %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>% 
  group_by(m, fit_index, de) %>%
  filter(sim_model != "p1m1",
         sim_model != "p2m1",
         sim_model != "p2m2") %>%  
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  #mutate(de = fct_explicit_na(de, na_level = "NA"),  
  #       de = fct_relevel(de, "NA", "0.405", "0.9", "1.5"))  %>% 
  ggplot(aes(x = de, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~m, labeller = labeller(de = function(x) paste("Direct Effects:", x))) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Direct Effects",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Direct Effect, Analysis Model, and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "de_m_fit.jpeg"), dpi="retina", bg = "white", height=4, width=8, units="in")


# P34 x M123 x DE x Fit
plot_data %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>% 
  filter(sim_model != "p1m1",
         sim_model != "p2m1",
         sim_model != "p2m2") %>% 
  group_by(de, p, fit_index, m) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = de, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_grid(p ~ m, labeller = label_value) +
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Direct Effect",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Direct Effect, Population and Analysis Models, and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "p34_m123_de_fit.jpeg"), dpi="retina", bg = "white", height=5, width=10, units="in")


# P34 x M123 x Sep x Fit
plot_data %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  filter(sim_model != "p1m1",
         sim_model != "p2m1",
         sim_model != "p2m2") %>%  
  group_by(separation, p, fit_index, m) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = separation, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_grid(p ~ m, labeller = label_value) +
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Separation",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Separation, Population and Analysis Models, and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "p34_m123_sep_fit.jpeg"), dpi="retina", bg = "white", height=5, width=10, units="in")



# P34 x M123 x Model x Fit
plot_data %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>% 
  mutate(model = toTitleCase(model)) %>% 
  filter(sim_model != "p1m1",
         sim_model != "p2m1",
         sim_model != "p2m2") %>%  
  group_by(model, p, fit_index, m) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = model, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_grid(p ~ m, labeller = label_value) +
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Measurement Model",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Measurement Model, Population and Analysis Models, and Model Selection Criterion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "p34_m123_model_fit.jpeg"), dpi="retina", bg = "white", height=5, width=10, units="in")
```


## Separation x *Condition* Bar

```{r}
# N
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  ggplot(aes(x = N, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Separation and Sample Size",
       x = "N",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(apa_colors_2, levels(as.factor(toTitleCase(plot_data$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )



# Class Proportion
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>%
  mutate(k_split = toTitleCase(k_split)) %>%
  ggplot(aes(x = k_split, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Separation and Class Proportion",
       x = "Class Proportion",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(apa_colors_2, levels(as.factor(toTitleCase(plot_data$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )


# DE
plot_data %>% 
  #filter(!is.na(de)) %>%  # Corrected filtering of NA values
  mutate(separation = toTitleCase(separation)) %>% 
  ggplot(aes(x = de, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Separation and Direct Effect",
       x = "DE",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(apa_colors_2, levels(as.factor(toTitleCase(plot_data$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )


# P
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>%
  ggplot(aes(x = p, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Separation and Population Model",
       x = "Population Model",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(apa_colors_2, levels(as.factor(toTitleCase(plot_data$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )


# M 
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>%
  ggplot(aes(x = m, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Separation and Analysis Model",
       x = "Analysis Model",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(apa_colors_2, levels(as.factor(toTitleCase(plot_data$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )


# Measurement Model
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  mutate(model = toTitleCase(model)) %>% 
  ggplot(aes(x = model, y = prop_correct, fill = as.factor(separation))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  labs(title = "Average Recovery Rate by Separation and Measurement Model",
       x = "Measurement Model",
       y = "Average Recovery Rate",
       fill = "Separation") +
  scale_fill_manual(values = setNames(apa_colors_2, levels(as.factor(toTitleCase(plot_data$separation))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
```


## Separation x Model Selection Criterion x *Condition* Lineplot

```{r}
# N
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  group_by(N, fit_index, separation) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = N, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~separation, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Sample Size (N)",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Model Selection Criterion, Separation, and Sample Size"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

# Class Proportion
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  mutate(k_split = toTitleCase(k_split)) %>% 
  group_by(k_split, fit_index, separation) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = k_split, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~separation, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Class Proportion",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Model Selection Criterion, Separation, and Class Proportion"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

# DE
plot_data %>% 
  filter(!is.na(de)) %>%  # Corrected filtering of NA values
  mutate(separation = toTitleCase(separation)) %>% 
  group_by(de, fit_index, separation) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = de, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~separation, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Direct Effect",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Model Selection Criterion, Separation, and Direct Effect"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

# P
plot_data %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>%
  mutate(separation = toTitleCase(separation)) %>% 
  group_by(p, fit_index, separation) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = p, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~separation, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Population Model",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Model Selection Criterion, Separation, and Population Model"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )


# M
plot_data %>% 
  mutate(m = toupper(m),
         p = toupper(p)) %>%
  mutate(separation = toTitleCase(separation)) %>% 
  group_by(m, fit_index, separation) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = m, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~separation, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Analysis Model",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Model Selection Criterion, Separation, and Analysis Model"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )


# Measurement Model
plot_data %>% 
  mutate(separation = toTitleCase(separation)) %>% 
  mutate(model = toTitleCase(model)) %>% 
  group_by(model, fit_index, separation) %>%
  summarise(
    mean_prop_correct = mean(prop_correct, na.rm = TRUE),
    se = sd(prop_correct, na.rm = TRUE) / sqrt(n())  # Standard error
  ) %>%
  ungroup() %>% 
  ggplot(aes(x = model, y = mean_prop_correct, color = as.factor(fit_index), group = as.factor(fit_index))) +
  geom_line(size = 1) +  # Solid line for APA consistency
  geom_point(size = 3) +  # Increase point size for readability
  geom_errorbar(aes(ymin = mean_prop_correct - se, ymax = mean_prop_correct + se), 
                width = 0.1, size = 0.7) +  # APA-style error bars
  facet_wrap(~separation, labeller = label_value) +  # Better facet labels
  scale_color_manual(values = apa_colors) +  # Use defined APA color palette
  labs(
    x = "Measurement Model",
    y = "Average Recovery Rates",
    color = "Model Selection Criterion",
    title = "Average Recovery Rates by Model Selection Criterion, Separation, and Measurement Model"
  ) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
```

## HeatMap

```{r, fig.width = 13, fig.height= 9}
data <- plot_data %>% mutate(condition_combo = paste(N, k_split, model, de, sep = "_")) %>% 
  mutate(condition_combo = fct_reorder(condition_combo, prop_correct, .fun = mean, .desc = TRUE))

ggplot(data, aes(x = fit_index, y = condition_combo, fill = prop_correct)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue") +
  theme_minimal() +
  labs(y = "Condition", fill = "Average Recovery Rate")
```


## N x P x M x Class Size x DE

```{r, fig.width = 13, fig.height= 9}
# P12 x M12 x N
plot_data %>% 
  mutate(m = toTitleCase(m),
         p = toTitleCase(p)) %>% 
  filter(!grepl("p3|p4", sim_model)) %>% 
  rename(`DE` = de) %>% 
  ggplot(aes(x = p, y = prop_correct, fill = as.factor(m))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  facet_wrap(~N) +
  labs(
    title = "Effect of Simulation Models and Sample Size",
    x = "Population Model",
    y = "Average Recovery Rate",
    fill = "Analysis Model"
  ) +
  scale_fill_manual(values = setNames(apa_colors, levels(as.factor(tools::toTitleCase(plot_data$m))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "p12_m12_N_bar.jpeg"), dpi="retina", bg = "white", units="in")


custom_labeller <- labeller(
  Sep = function(x) stringr::str_to_title(x),  
  N = label_both,
 `DE` = label_both
)

BIC_only %>% 
  mutate(m = toTitleCase(m),
         p = toTitleCase(p),
         separation = toTitleCase(separation),
         de = factor(case_when(
           de == 0.405 ~ "Small",
           de == 0.9 ~ "Medium",
           de == 1.5 ~ "Large",
           TRUE ~ as.character(de)  # Keeps other values unchanged
         ),
         levels = c("Small", "Medium", "Large"))) %>% 
  filter(sim_model != "p1m1",
         sim_model != "p2m1",
         sim_model != "p2m2") %>%
  rename(`DE` = de,
         `Sep` = separation) %>% 
  ggplot(aes(x = p, y = prop_correct, fill = as.factor(m))) +
  stat_summary(fun = mean, geom = "bar", 
               position = position_dodge(0.9), 
               color = "black") +
  stat_summary(fun.data = mean_se, geom = "errorbar", 
               position = position_dodge(0.9), 
               width = 0.2, color = "black") +
  facet_grid(`DE` ~ N + `Sep`, labeller = custom_labeller) +
  labs(
    title = "Average Recovery Rates by Population and Analysis Models, Sample Size, Separation and Direct Effects",
    x = "Population Model",
    y = "Average Recovery Rate",
    fill = "Analysis Model"
  ) +
  scale_fill_manual(values = setNames(analysis_model_colors, levels(as.factor(tools::toTitleCase(BIC_only$m))))) +
  ylim(0,1) +
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 16, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 14, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 12, face = "bold"),  
    axis.text = element_text(size = 12, color = "black"),  
    strip.text = element_text(size = 12, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 11),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "p34_m123_N_sep_de_bar.jpeg"), dpi="retina", width = 12, bg = "white", units="in")

```

