---
title: "Dissertation Simulation Data"
format:
  html:
    code-fold: true
    code-summary: "Show the code"
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE) 
```

```{r}
library(tidyverse)
library(MplusAutomation)
library(here)
library(glue)
library(reshape2)
library(cowplot)
```

# Complex (10 items, 5 classes)

## Ideal Separation

### Generate Single Dataset

```{r, eval = FALSE}
sim_class  <- mplusObject(
  
  TITLE = "Complex, Ideal Separation", 
  
  MONTECARLO = "NAMES = u1-u10;
    	GENERATE = u1-u10(1);
    	CATEGORICAL = u1-u10;
    	GENCLASSES = c(5);
    	CLASSES = c(5);
    	NOBSERVATIONS = 500; 
    	SEED = 1495;
    	NREPS = 1;
      REPSAVE = all;
      SAVE= p1m1_N500_C5_even_complex_ideal_results*.csv;",
  
  ANALYSIS = 
    "TYPE = MIXTURE;
     STARTS = 200 100;",
  
  MODELPOPULATION = 
    "%OVERALL%
    
    [c#1*0];
    [c#2*0];
    [c#3*0];
    [c#4*0];    
  	
    %C#1%

  	 [u1$1*-2 u2$1*-2 u3$1*-2 u4$1*-2 u5$1*-2
  	 u6$1*-2 u7$1*-2 u8$1*-2 u9$1*-2 u10$1*-2];

     %C#2%

  	 [u1$1*-2 u2$1*-2 u3$1*-2 u4$1*-2 u5$1*-2
  	 u6$1*2 u7$1*2 u8$1*2 u9$1*2 u10$1*2];

     %C#3%

  	 [u1$1*2 u2$1*2 u3$1*2 u4$1*-2 u5$1*-2
  	 u6$1*-2 u7$1*2 u8$1*2 u9$1*2 u10$1*2];

     %C#4%

  	 [u1$1*2 u2$1*2 u3$1*2 u4$1*2 u5$1*2
  	 u6$1*-2 u7$1*-2 u8$1*-2 u9$1*-2 u10$1*-2];

     %C#5%

  	 [u1$1*2 u2$1*2 u3$1*2 u4$1*2 u5$1*2
     u6$1*2 u7$1*2 u8$1*2 u9$1*2 u10$1*2];",
  
  OUTPUT = "tech9 tech11;")

sim_fit <- mplusModeler(sim_class, 
                        dataout=here("models","complex_ideal.dat"),
                        modelout=here("models", "complex_ideal.inp"), 
                        check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Estimate Model

```{r, eval = FALSE}
# Read in data

data <- read.delim(here("models", "p1m1_N500_C5_even_complex_ideal_results1.csv"), sep = "", header = FALSE)
names(data) <- c("u1", "u2", "u3", "u4", "u5", "u6", "u7", "u8", "u9", "u10", "c")
summary(data)


# Estimate model

lca_enum  <- mplusObject(
  
  TITLE = "Complex, Ideal, 5-Class", 
  
  VARIABLE = 
    "categorical = u1-u10;  
     usevar = u1-u10;
     classes = c(5);",
  
  ANALYSIS = 
    "estimator = mlr; 
    type = mixture;
    starts = 500 100;",
  
  OUTPUT = "sampstat;",
  
  usevariables = colnames(data),
  rdata = data)

lca_enum_fit <- mplusModeler(lca_enum, 
                             dataout=glue(here("models","complex_ideal_c5.dat")),
                             modelout=glue(here("models", "complex_ideal_c5.inp")),
                             check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Evaluate Separation

```{r}
source(here("functions","plot_lca"))
source(here("functions", "diagnostics_table"))

model <- readModels(here("models", "complex_ideal_c5.out"))


simple_diagnostics_table(model)
class_sep(model)
sep_percent(model)
prob_table(model)
prob_percent(model)
plot_lca(model)
```

### Plot Logits

```{r}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(-2,-2,-2,-2,-2,-2,-2,-2,-2,-2),
  C2 = c(-2,-2,-2,-2,-2,2,2,2,2,2),
  C3 = c(2,2,2,-2,-2,-2,2,2,2,2),
  C4 = c(2,2,2,2,2,-2,-2,-2,-2,-2),
  C5 = c(2,2,2,2,2,2,2,2,2,2)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:10)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line() +
  geom_hline(yintercept = c(0.7, 0.3))+
  geom_point() +
  labs(title = "Ideal Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  ylim(0,1) +
  theme_cowplot()


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "High Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "ideal_complex_line_plot.png"), dpi = "retina", width = 5, height = 4, bg = "white",  units="in")
```

## Realistic Separation

### Generate Single Dataset

```{r, eval = FALSE}
sim_class  <- mplusObject(
  
  TITLE = "Complex, Realistic Separation", 
  
  MONTECARLO = "NAMES = u1-u10;
    	GENERATE = u1-u10(1);
    	CATEGORICAL = u1-u10;
    	GENCLASSES = c(5);
    	CLASSES = c(5);
    	NOBSERVATIONS = 500; 
    	SEED = 1495;
    	NREPS = 1;
      REPSAVE = all;
      SAVE= p1m1_N500_C5_even_complex_real_results*.csv;",
  
  ANALYSIS = 
    "TYPE = MIXTURE;
     STARTS = 200 100;",
  
  MODELPOPULATION = 
    "%OVERALL%
    
    [c#1*0];
    [c#2*0];
    [c#3*0];
    [c#4*0];    
  	
    %C#1%
    
    [u1$1*3.19064 u2$1*3.10788 u3$1*3.83448 u4$1*3.86343 u5$1*2.00700 
     u6$1*2.92895 u7$1*1.43653 u8$1*2.75844 u9$1*3.01256 u10$1*1.89987];

    %C#2%
    
    [u1$1*1.16631 u2$1*-0.15619 u3$1*3.77549 u4$1*-0.51226 u5$1*-1.58301 
     u6$1*0.11202 u7$1*-2.15707 u8$1*0.57930 u9$1*-0.28985 u10$1*-0.19538];

    %C#3%
    
    [u1$1*-0.56244 u2$1*-0.06104 u3$1*-0.74264 u4$1*0.58389 u5$1*-1.44290 
     u6$1*-15 u7$1*0.17762 u8$1*2.74127 u9$1*1.67876 u10$1*2.60714];

    %C#4%
    
    [u1$1*-2.13783 u2$1*-3.46779 u3$1*-3.17454 u4$1*-2.12725 u5$1*-2.57868 
     u6$1*-3.62206 u7$1*-3.27125 u8$1*-0.67695 u9$1*-1.86035 u10$1*-1.42219];

    %C#5%
    
    [u1$1*-0.69130 u2$1*-1.27803 u3$1*-0.05214 u4$1*1.48891 u5$1*1.99572 
     u6$1*1.75719 u7$1*-0.18973 u8$1*1.46395 u9$1*0.41521 u10$1*0.38082];",
  
  OUTPUT = "tech9 tech11;")

sim_fit <- mplusModeler(sim_class, 
                        dataout=here("models","complex_real.dat"),
                        modelout=here("models", "complex_real.inp"), 
                        check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Estimate Model

```{r, eval = FALSE}
# Read in data

data <- read.delim(here("models", "p1m1_N500_C5_even_complex_real_results1.csv"), sep = "", header = FALSE)
names(data) <- c("u1", "u2", "u3", "u4", "u5", "u6", "u7", "u8", "u9", "u10", "c")
summary(data)


# Estimate model

lca_enum  <- mplusObject(
  
  TITLE = "Complex, Real, 5-Class", 
  
  VARIABLE = 
    "categorical = u1-u10;  
     usevar = u1-u10;
     classes = c(5);",
  
  ANALYSIS = 
    "estimator = mlr; 
    type = mixture;
    starts = 500 100;",
  
  OUTPUT = "sampstat;",
  
  usevariables = colnames(data),
  rdata = data)

lca_enum_fit <- mplusModeler(lca_enum, 
                             dataout=glue(here("models","complex_real_c5.dat")),
                             modelout=glue(here("models", "complex_real_c5.inp")),
                             check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Evaluate Separation

```{r}
source(here("functions","plot_lca"))
source(here("functions", "diagnostics_table"))

model <- readModels(here("models", "complex_real_c5.out"))


simple_diagnostics_table(model)
class_sep(model)
sep_percent(model)
prob_table(model)
prob_percent(model)
plot_lca(model)
```

### Plot Logits

```{r}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(3.19064, 3.10788, 3.83448, 3.86343, 2.00700, 2.92895, 1.43653, 2.75844, 3.01256, 1.89987),
  C2 = c(1.16631, -0.15619, 3.77549, -0.51226, -1.58301, 0.11202, -2.15707, 0.57930, -0.28985, -0.19538),
  C3 = c(-0.56244, -0.06104, -0.74264, 0.58389, -1.44290, -15.0, 0.17762, 2.74127, 1.67876, 2.60714),
  C4 = c(-2.13783, -3.46779, -3.17454, -2.12725, -2.57868, -3.62206, -3.27125, -0.67695, -1.86035, -1.42219),
  C5 = c(-0.69130, -1.27803, -0.05214, 1.48891, 1.99572, 1.75719, -0.18973, 1.46395, 0.41521, 0.38082)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:10)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line() +
  geom_hline(yintercept = c(0.7, 0.3))+
  geom_point() +
  labs(title = "Realistic Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  ylim(0,1) +
  theme_cowplot()


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Realistic Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
ggsave(here("figures", "real_complex_line_plot.png"), dpi = "retina", width = 5, height = 4, bg = "white",  units="in")
```

## Unstable Separation

### Generate Single Dataset

```{r, eval = FALSE}
sim_class  <- mplusObject(
  
  TITLE = "Complex, Unstable Separation", 
  
  MONTECARLO = "NAMES = u1-u10;
    	GENERATE = u1-u10(1);
    	CATEGORICAL = u1-u10;
    	GENCLASSES = c(5);
    	CLASSES = c(5);
    	NOBSERVATIONS = 500; 
    	SEED = 1495;
    	NREPS = 1;
      REPSAVE = all;
      SAVE= p1m1_N500_C5_even_complex_unstable_results*.csv;",
  
  ANALYSIS = 
    "TYPE = MIXTURE;
     STARTS = 200 100;",
  
  MODELPOPULATION = 
    "%OVERALL%
    
    [c#1*0];
    [c#2*0];
    [c#3*0];
    [c#4*0];    
  	
    %C#1%
    
    [u1$1*1.5 u2$1*1.6 u3$1*2.0 u4$1*1.2 u5$1*1.4 
     u6$1*1.3 u7$1*1.1 u8$1*1.2 u9$1*1.5 u10$1*1.3];

    %C#2%
    
    [u1$1*1.0 u2$1*0.8 u3$1*1.1 u4$1*0.4 u5$1*0.2 
     u6$1*0.6 u7$1*0.3 u8$1*0.4 u9$1*0.1 u10$1*0.0];

    %C#3%
    
    [u1$1*0.5 u2$1*0.2 u3$1*0.4 u4$1*0.3 u5$1*0.1 
     u6$1*-0.1 u7$1*-0.3 u8$1*0.2 u9$1*0.3 u10$1*0.0];

    %C#4%
    
    [u1$1*-0.2 u2$1*-0.5 u3$1*-0.3 u4$1*-0.4 u5$1*-0.6 
     u6$1*-0.5 u7$1*-0.3 u8$1*-0.2 u9$1*-0.1 u10$1*-0.4];

    %C#5%
    
    [u1$1*0.1 u2$1*0.0 u3$1*0.2 u4$1*0.1 u5$1*0.2 
     u6$1*0.0 u7$1*-0.1 u8$1*0.2 u9$1*0.1 u10$1*0.0];",
  
  OUTPUT = "tech9 tech11;")

sim_fit <- mplusModeler(sim_class, 
                        dataout=here("models","complex_unstable.dat"),
                        modelout=here("models", "complex_unstable.inp"), 
                        check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Estimate Model

```{r, eval = FALSE}
# Read in data

data <- read.delim(here("models", "p1m1_N500_C5_even_complex_unstable_results1.csv"), sep = "", header = FALSE)
names(data) <- c("u1", "u2", "u3", "u4", "u5", "u6", "u7", "u8", "u9", "u10", "c")
summary(data)


# Estimate model

lca_enum  <- mplusObject(
  
  TITLE = "Complex, Unstable, 5-Class", 
  
  VARIABLE = 
    "categorical = u1-u10;  
     usevar = u1-u10;
     classes = c(5);",
  
  ANALYSIS = 
    "estimator = mlr; 
    type = mixture;
    starts = 500 100;",
  
  OUTPUT = "sampstat;",
  
  usevariables = colnames(data),
  rdata = data)

lca_enum_fit <- mplusModeler(lca_enum, 
                             dataout=glue(here("models","complex_unstable_c5.dat")),
                             modelout=glue(here("models", "complex_unstable_c5.inp")),
                             check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Evaluate Separation

```{r}
source(here("functions","plot_lca"))
source(here("functions", "diagnostics_table"))

model <- readModels(here("models", "complex_unstable_c5.out"))


simple_diagnostics_table(model)
class_sep(model)
sep_percent(model)
prob_table(model)
prob_percent(model)
plot_lca(model)
```

### Plot Logits

```{r}
# Define the negative logits for the first example as a list
logits <- data.frame(
  C1 = c(1.5, 1.6, 2.0, 1.2, 1.4, 1.3, 1.1, 1.2, 1.5, 1.3),
  C2 = c(1.0, 0.8, 1.1, 0.4, 0.2, 0.6, 0.3, 0.4, 0.1, 0.0),
  C3 = c(0.5, 0.2, 0.4, 0.3, 0.1, -0.1, -0.3, 0.2, 0.3, 0.0),
  C4 = c(-0.2, -0.5, -0.3, -0.4, -0.6, -0.5, -0.3, -0.2, -0.1, -0.4),
  C5 = c(0.1, 0.0, 0.2, 0.1, 0.2, 0.0, -0.1, 0.2, 0.1, 0.0)
)

# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:10)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line() +
  geom_hline(yintercept = c(0.7, 0.3))+
  geom_point() +
  labs(title = "Unstable Separation (Complex)",
       x = "Indicators", y = "Probabilities") +
  ylim(0,1) +
  theme_cowplot()
```

# Simple (6 items, 4 classes)

## Ideal Separation

### Generate Single Dataset

```{r, eval = FALSE}
sim_class  <- mplusObject(
  
  TITLE = "Complex, Ideal Separation", 
  
  MONTECARLO = "NAMES = u1-u6;
    	GENERATE = u1-u6(1);
    	CATEGORICAL = u1-u6;
    	GENCLASSES = c(4);
    	CLASSES = c(4);
    	NOBSERVATIONS = 500; 
    	SEED = 1495;
    	NREPS = 1;
      REPSAVE = all;
      SAVE= p1m1_N500_C4_even_simple_ideal_results*.csv;",
  
  ANALYSIS = 
    "TYPE = MIXTURE;
     STARTS = 200 100;",
  
  MODELPOPULATION = 
    "%OVERALL%
    
    [c#1*0];
    [c#2*0];
    [c#3*0];
  	
     %C#1%

  	 [u1$1*-2 u2$1*-2 u3$1*-2
  	 u4$1*-2 u5$1*-2 u6$1*-2];

     %C#2%

  	 [u1$1*-2 u2$1*-2 u3$1*-2
  	 u4$1*2 u5$1*2 u6$1*2];
  	
     %C#3%

  	 [u1$1*2 u2$1*2 u3$1*2
  	 u4$1*-2 u5$1*-2 u6$1*-2];
  
     %C#4%

  	 [u1$1*2 u2$1*2 u3$1*2
  	 u4$1*2 u5$1*2 u6$1*2];",
  
  OUTPUT = "tech9 tech11;")

sim_fit <- mplusModeler(sim_class, 
                        dataout=here("models","simple_ideal.dat"),
                        modelout=here("models", "simple_ideal.inp"), 
                        check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Estimate Model

```{r, eval = FALSE}
# Read in data

data <- read.delim(here("models", "p1m1_N500_C4_even_simple_ideal_results1.csv"), sep = "", header = FALSE)
names(data) <- c("u1", "u2", "u3", "u4", "u5", "u6", "c")
summary(data)


# Estimate model

lca_enum  <- mplusObject(
  
  TITLE = glue("Simple, Ideal, 4-Class"), 
  
  VARIABLE = glue(
    "categorical = u1-u6;  
     usevar = u1-u6;
     classes = c(4);"),
  
  ANALYSIS = 
    "estimator = mlr; 
    type = mixture;
    starts = 500 100;",
  
  OUTPUT = "sampstat;",
  
  usevariables = colnames(data),
  rdata = data)

lca_enum_fit <- mplusModeler(lca_enum, 
                             dataout=glue(here("models","simple_ideal_c4.dat")),
                             modelout=glue(here("models", "simple_ideal_c4.inp")),
                             check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Evaluate Separation

```{r}
source(here("functions","plot_lca"))
source(here("functions", "diagnostics_table"))

model <- readModels(here("models", "simple_ideal_c4.out"))


simple_diagnostics_table(model)
class_sep(model)
sep_percent(model)
prob_table(model)
prob_percent(model)
plot_lca(model)
```

### Plot Logits

```{r}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(-2,-2,-2,-2,-2,-2),
  C2 = c(-2,-2,-2,2,2,2),
  C3 = c(2,2,2,-2,-2,-2),
  C4 = c(2,2,2,2,2,2)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:6)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line() +
  geom_hline(yintercept = c(0.7, 0.3))+
  geom_point() +
  labs(title = "Ideal Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  ylim(0,1) +
  theme_cowplot()


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Ideal Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )

ggsave(here("figures", "ideal_simple_line_plot.png"), dpi = "retina", width = 5, height = 4, bg = "white",  units="in")
```

## Realistic Separation

### Generate Single Dataset

```{r, eval = FALSE}
sim_class  <- mplusObject(
  
  TITLE = "Simple, Realistic Separation", 
  
  MONTECARLO = "NAMES = u1-u6;
    	GENERATE = u1-u6(1);
    	CATEGORICAL = u1-u6;
    	GENCLASSES = c(4);
    	CLASSES = c(4);
    	NOBSERVATIONS = 500; 
    	SEED = 1495;
    	NREPS = 1;
      REPSAVE = all;
      SAVE= p1m1_N500_C4_even_simple_real_results*.csv;",
  
  ANALYSIS = 
    "TYPE = MIXTURE;
     STARTS = 200 100;",
  
  MODELPOPULATION = 
    "%OVERALL%
    
    [c#1*0];
    [c#2*0];
    [c#3*0];
  	
    %C#1%
    
    [u1$1*-2.1 u2$1*-2.120 u3$1*-2.737 u4$1*-4.172 u5$1*-1.591 
     u6$1*-3.187];

    %C#2%
    
    [u1$1*-0.2 u2$1*-0.329 u3$1*-0.127 u4$1*-1.199 u5$1*1.591 
     u6$1*1.710];

    %C#3%
    
    [u1$1*-1.5 u2$1*-0.738 u3$1*0.888 u4$1*0.964 u5$1*0.039 
     u6$1*-15.000];

    %C#4%
    
    [u1$1*1 u2$1*1.547 u3$1*3.910 u4$1*2.382 u5$1*3.483 
     u6$1*15.000];",
  
  OUTPUT = "tech9 tech11;")

sim_fit <- mplusModeler(sim_class, 
                        dataout=here("models","simple_real.dat"),
                        modelout=here("models", "simple_real.inp"), 
                        check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Estimate Model

```{r, eval = FALSE}
# Read in data

data <- read.delim(here("models", "p1m1_N500_C4_even_simple_real_results1.csv"), sep = "", header = FALSE)
names(data) <- c("u1", "u2", "u3", "u4", "u5", "u6", "c")
summary(data)


# Estimate model

lca_enum  <- mplusObject(
  
  TITLE = glue("Simple, Real, 4-Class"), 
  
  VARIABLE = glue(
    "categorical = u1-u6;  
     usevar = u1-u6;
     classes = c(4);"),
  
  ANALYSIS = 
    "estimator = mlr; 
    type = mixture;
    starts = 500 100;",
  
  OUTPUT = "sampstat;",
  
  usevariables = colnames(data),
  rdata = data)

lca_enum_fit <- mplusModeler(lca_enum, 
                             dataout=glue(here("models","simple_real_c4.dat")),
                             modelout=glue(here("models", "simple_real_c4.inp")),
                             check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Evaluate Separation

```{r}
source(here("functions","plot_lca"))
source(here("functions", "diagnostics_table"))

model <- readModels(here("models", "simple_real_c4.out"))


simple_diagnostics_table(model)
class_sep(model)
sep_percent(model)
prob_table(model)
prob_percent(model)
plot_lca(model)
```

### Plot Logits

```{r}
# Define the logits for the first example as a list
logits <- data.frame(
  C1 = c(-2.1, -2.120, -2.737, -4.172, -1.591, -3.187),
  C2 = c(-.2, -0.329, -0.127, -1.199, 1.591, 1.710),
  C3 = c(-1.5, -0.738, 0.888, 0.964, 0.039, -15.000),
  C4 = c(1, 1.547, 3.910, 2.382, 3.483, 15.000)
)


# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:6)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line() +
  geom_hline(yintercept = c(0.7, 0.3))+
  geom_point() +
  labs(title = "Realistic Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  ylim(0,1) +
  theme_cowplot()


# Define APA-appropriate color palette (muted colors)
apa_colors <- c("aBIC" = "#1b9e77", "AWE" = "#d95f02", "BIC" = "#7570b3", 
                "CAIC" = "#e7298a", "VLMR" = "#66a61e")

ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line(size = 1) + 
  geom_point(size = 3) +
  geom_hline(yintercept = c(0.7, 0.3))+
  labs(title = "Realistic Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  scale_color_manual(values = setNames(apa_colors, unique(df$class))) +
  ylim(0,1)+
  theme_bw() +  
  theme(
    text = element_text(family = "serif", size = 18, color = "black"),  # APA requires serif font
    plot.title = element_text(size = 17, color = "black", face = "bold", hjust = 0.5),  # Center-align title
    axis.title = element_text(size = 15, face = "bold"),  
    axis.text = element_text(size = 15, color = "black"),  
    strip.text = element_text(size = 15, face = "bold"),  # Facet labels bold
    legend.title = element_text(size = 15, face = "bold"),  
    legend.text = element_text(size = 15),  
    legend.position = "bottom",  # Maintain clear placement for APA style
    legend.direction = "horizontal"
  )
ggsave(here("figures", "real_simple_line_plot.png"), dpi = "retina", width = 5, height = 4, bg = "white",  units="in")
```

## Unstable Separation

### Generate Single Dataset

```{r, eval = FALSE}
sim_class  <- mplusObject(
  
  TITLE = "Simple, Unstable Separation", 
  
  MONTECARLO = "NAMES = u1-u6;
    	GENERATE = u1-u6(1);
    	CATEGORICAL = u1-u6;
    	GENCLASSES = c(4);
    	CLASSES = c(4);
    	NOBSERVATIONS = 500; 
    	SEED = 1495;
    	NREPS = 1;
      REPSAVE = all;
      SAVE= p1m1_N500_C4_even_simple_unstable_results*.csv;",
  
  ANALYSIS = 
    "TYPE = MIXTURE;
     STARTS = 200 100;",
  
  MODELPOPULATION = 
    "%OVERALL%
    
    [c#1*0];
    [c#2*0];
    [c#3*0];
  
    %C#1%
    
    [u1$1*-0.5 u2$1*-0.3 u3$1*-0.2 u4$1*0.1 u5$1*0.3 
     u6$1*0.2];

    %C#2%
    
    [u1$1*0.1 u2$1*-0.1 u3$1*0.2 u4$1*-0.2 u5$1*-0.1 
     u6$1*0.0];

    %C#3%
    
    [u1$1*0.0 u2$1*0.1 u3$1*-0.1 u4$1*0.2 u5$1*-0.3 
     u6$1*-0.2];

    %C#4%
    
    [u1$1*0.5 u2$1*0.6 u3$1*0.4 u4$1*0.7 u5$1*0.5 
     u6$1*0.6];",
  
  OUTPUT = "tech9 tech11;")

sim_fit <- mplusModeler(sim_class, 
                        dataout=here("models","simple_unstable.dat"),
                        modelout=here("models", "simple_unstable.inp"), 
                        check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Estimate Model

```{r, eval = FALSE}
# Read in data

data <- read.delim(here("models", "p1m1_N500_C4_even_simple_unstable_results1.csv"), sep = "", header = FALSE)
names(data) <- c("u1", "u2", "u3", "u4", "u5", "u6", "c")
summary(data)


# Estimate model

lca_enum  <- mplusObject(
  
  TITLE = glue("Simple, Unstable, 4-Class"), 
  
  VARIABLE = glue(
    "categorical = u1-u6;  
     usevar = u1-u6;
     classes = c(4);"),
  
  ANALYSIS = 
    "estimator = mlr; 
    type = mixture;
    starts = 500 100;",
  
  OUTPUT = "sampstat;",
  
  usevariables = colnames(data),
  rdata = data)

lca_enum_fit <- mplusModeler(lca_enum, 
                             dataout=glue(here("models","simple_unstable_c4.dat")),
                             modelout=glue(here("models", "simple_unstable_c4.inp")),
                             check=TRUE, run = TRUE, hashfilename = FALSE)
```

### Evaluate Separation

```{r}
source(here("functions","plot_lca"))
source(here("functions", "diagnostics_table"))

model <- readModels(here("models", "simple_unstable_c4.out"))


simple_diagnostics_table(model)
class_sep(model)
sep_percent(model)
prob_table(model)
prob_percent(model)
plot_lca(model)
```

### Plot Logits

```{r}
# Define the negative logits for the first example as a list
logits <- data.frame(
  C1 = c(-0.5, -0.3, -0.2, 0.1, 0.3, 0.2),  # Less negative, closer to 0
  C2 = c(0.1, -0.1, 0.2, -0.2, -0.1, 0.0),  # Small fluctuations, minimal difference
  C3 = c(0.0, 0.1, -0.1, 0.2, -0.3, -0.2),  # More overlap, close to 0
  C4 = c(0.5, 0.6, 0.4, 0.7, 0.5, 0.6)       # Small positive values, close to 0
)

# Convert logits to probabilities using the sigmoid function
sigmoid <- function(x) {
  1 / (1 + exp(x))
}


probabilities <- lapply(logits, sigmoid) %>% 
  as.data.frame() 

df <- probabilities %>% 
  mutate(Indicator = rep(1:6)) %>%
  pivot_longer(cols = -c(Indicator), names_to = "Class", values_to = "Probability")


ggplot(df, aes(x = factor(Indicator), y = Probability, group = Class, color = Class)) +
  geom_line() +
  geom_hline(yintercept = c(0.7, 0.3))+
  geom_point() +
  labs(title = "Unstable Separation (Simple)",
       x = "Indicators", y = "Probabilities") +
  ylim(0,1) +
  theme_cowplot()
```
